A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-08-23 abstract.Rmd
remove passive voice #26

In this tutorial, we describe a principled workflow to ensure long-term reproducibility of R-based data analyses. The workflow is based on established tools and practices from software engineering. It combines the benefits of various open-source software tools including Rmarkdown, git, make and docker whose interplay ensures seamless integration of version management, (APA-conformable) dynamic report generation and full cross-platform and long-term computational reproducibility. The workflow ensures meeting the primary goals that 1) the reporting of analysis results is perfectly consistent with the actual analysis results (dynamic report generation), the analysis exactly reproduces at a later time even if the computing and software platform is updated or changed (computational reproducibility), and 3) changes at any time (during development and post-publication) are tracked, tagged, and documented while earlier versions of both data and code remain accessible. While dynamic document generation is increasingly recognized as a tool to ensure reproducibility, we demonstrate with practical examples that dynamic documents alone are not sufficient to ensure long-term computational reproducibility.

>>>>

In this tutorial, we describe a principled workflow to ensure long-term reproducibility of R-based data analyses. The workflow utilizes established tools and practices from software engineering. It combines the benefits of various open-source software tools including Rmarkdown, git, make and docker whose interplay ensures seamless integration of version management, (APA-conformable) dynamic report generation and full cross-platform and long-term computational reproducibility. The workflow ensures meeting the primary goals that 1) the reporting of analysis results is perfectly consistent with the actual analysis results (dynamic report generation), the analysis exactly reproduces at a later time even if the computing and software platform is updated or changed (computational reproducibility), and 3) changes at any time (during development and post-publication) are tracked, tagged, and documented while earlier versions of both data and code remain accessible. While the research community recognizes dynamic document generation as a tool to ensure reproducibility, we demonstrate with practical examples that dynamic documents alone are not sufficient to ensure long-term computational reproducibility.
